A Fully Abstract Game Semantics for Countable Nondeterminism

### 2018-01-29 cones/paper/cones.tex
Fixed incorrect name.

We define a game $\oc A$ as follows.  
The arena for $\oc A$ is the same as the arena for $A$, but the set of plays is given by
\[
  P_{\oc A} = \{s\in L_A\suchthat s\vert_m\in P_A\text{ for each initial move $m$}\}\,.
  \]
There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\coh\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.  
This construction is essentially the co-Kleisli category on a comonad given by $\oc$, but certain technical issues prevent us from presenting it in this way.
See \cite{SamsonGuyIAPassive} for full details.

>>>>

We define a game $\oc A$ as follows.  
The arena for $\oc A$ is the same as the arena for $A$, but the set of plays is given by
\[
  P_{\oc A} = \{s\in L_A\suchthat s\vert_m\in P_A\text{ for each initial move $m$}\}\,.
  \]
There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\mathsf{coh}\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.  
This construction is essentially the co-Kleisli category on a comonad given by $\oc$, but certain technical issues prevent us from presenting it in this way.
See \cite{SamsonGuyIAPassive} for full details.
